---
title: Test Rmarkdown File
author: Jon Durbin
date: '2018-11-17'
slug: test-rmarkdown-file
categories:
  - R
  - Rmarkdown
tags:
  - plot
  - ggplot
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache = TRUE, echo=TRUE, fig.asp=0.68)
library(tidyverse)
library(reticulate)
use_python("/usr/bin/python3")
knitr::knit_engines$set(python = reticulate::eng_python)
```

## My first page!

**I have my own website now**

Look at this graph

```{r first_graph, fig.width=5}
ggplot(mtcars) +
  geom_point(aes(x=mpg, y=wt, size=hp))

# gcd - r version
gcd <- function(a,b) {
  if (b == 0) {
    return(abs(a))
  } else {
    return(gcd(b, a %% b))
  }
}
c(gcd(5,16),gcd(5,15))

```

I can put python scripts here too!

```{python using_python}
def gcd(a, b):
  if b == 0:
    return a
  else:
    return gcd(b, a % b)
  
print(gcd(5,16), gcd(5,15))
```
NOTE TO SELF:

  * Set the chunk options for a python chunk like `{python <CHUNK_NAME>}`. In the setup chunk, use the following lines:

```
library(reticulate)

# this option may not be necessary, but it makes me feel more confident
use_python("/usr/bin/python3")

knitr::knit_engines$set(python = reticulate::eng_python)
```

***

I plan on putting my resume in the overhead bar of links. The problem is that it's in a `.docx`, and I don't know if a way to convert that file type to `.html`. If I put a link to the `.docx` file in the header, it prompts a download, which I don't think I want.
